---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# contribution

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ShixiangWang/contribution?branch=master&svg=true)](https://ci.appveyor.com/project/ShixiangWang/contribution)
[![Travis build status](https://travis-ci.org/ShixiangWang/contribution.svg?branch=master)](https://travis-ci.org/ShixiangWang/contribution)
[![CRAN status](https://www.r-pkg.org/badges/version/contribution)](https://cran.r-project.org/package=contribution)
<!-- badges: end -->

The goal of **contribution** is to generate **contribution table** for credit assignment in a project. 
This is inspired by Nick Steinmetz (see twitter <https://twitter.com/SteinmetzNeuro/status/1147241138291527681>). 

> Authors contributions sections are new and still don’t appear in many journals, but can be improved. Rather than text listing each author’s contributions, the same data can be presented as a table with rows corresponding to contributions and columns for each author.
>
> Advantages include: 
>
> 1. Graphics are faster and easier to comprehend. They are also easier to locate in the document.
>
> 2. This format can be readily augmented with additional information, such as distinguishing between ‘major’ and ‘minor’ contributions of each type. Here, it makes clear that Warren had a much bigger role in data analysis than Tirin and me, which is a more accurate attribution.
>
> 3. This format can be read as easily in either direction, answering both "Who did X?" and "What did person Y do?" equally. 
>
> 4. This format lends itself to a nice extension for including your author contribution information on your CV: a similar table where each column is one of your papers.
>
>
> A difficulty with this is the diversity of terminology used, which would be helped by refinement and more widespread adoption of the CRediT framework (https://www.casrai.org/credit.html ). 


## Installation

~~You can install the released version of contribution from [CRAN](https://CRAN.R-project.org) with~~:

``` r
install.packages("contribution")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ShixiangWang/contribution")
```


## Example

### Basic

This is a basic example which shows you how to plot a simple contribution table:

```{r example}
library(contribution)
data("demo")
demo
```

```{r}
generate(demo)
```

The **white** box represents **no contribution**, the **grey** box represents **some contribution**, and the **black** box
represents **many contribution**.

The table is nice, easy to read. The result is a `ggplot` object, so you can modify in your way!

You can also use other colors and `scale_fill_*` function from **ggplot2** to map colors

```{r}
library(ggplot2)
generate(demo, text_angle_x = 20, color_map = scale_fill_brewer(palette ="Oranges"))
generate(demo, text_angle_x = 20, color_map = scale_fill_brewer(palette ="Set1"))
```

It is not easy to see the meaning of color, so show the legend.

```{r}
generate(demo, text_angle_x = 20, color_map = scale_fill_brewer(palette ="Set1"), show_legend = TRUE)
```

### CRediT

**CRediT** can help assign the role, this data has been stored in this package.

```{r}
data("CRediT")
```

Show whole table.

```{r}
knitr::kable(CRediT)
```

## To do

* Support special symbol for indicating equal work in a project/paper
* Support numeric contributions
* Support GitHub API to grep contributions for projects
* A shiny or addin of RStudio, maybe?

