---
title: "A Tiny Contribution Table Generator Based on ggplot2"
author: "Shixiang Wang \\
        ShanghaiTech. University"
date: "`r Sys.Date()`"

output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{A Tiny Contribution Table Generator Based on ggplot2}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of **contribution** is to generate **contribution table** for credit assignment in a project. 
This is inspired by Nick Steinmetz (see twitter <https://twitter.com/SteinmetzNeuro/status/1147241138291527681>). 

> Authors contributions sections are new and still don’t appear in major journals, but can be improved. Rather than text listing each author’s contributions, the same data can be presented as a table with rows corresponding to contributions and columns for each author.
>
> Advantages include: 
>
> 1. Graphics are faster and easier to comprehend. They are also easier to locate in the document.
>
> 2. This format can be readily augmented with additional information, such as distinguishing between ‘major’ and ‘minor’ contributions of each type.
>
> 3. This format can be read as easily in either direction, answering both "Who did X?" and "What did person Y do?" equally. 
>
> 4. This format lends itself to a nice extension for including your author contribution information on your CV: a similar table where each column is one of your papers.
>
>
> A difficulty with this is the diversity of terminology used, which would be helped by refinement and more widespread adoption of the CRediT framework (https://www.casrai.org/credit.html ). 

## Feature

* Support table type
  * 3-level contribution (i.e. 'None', 'Minor' and 'Major')
  * numeric contribution
* Dataset `palette` contains 27 color maps


## Installation

You can install the released version of contribution from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("contribution")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ShixiangWang/contribution")
```

## Basic example

This is a basic example which shows you how to plot a simple contribution table:

```{r example}
library(contribution)
data("demo")
demo
```

The accepted data format is a `data.frame` whose first column show the `role` and the other 
columns show the people or projects. This format is easy to create using R or other tools like Excel. 

For a 3-level contribution table, only `Minor` and `Major` are valid, a `NA` value should put 
in cell for no contribution.

```{r, fig.height=3}
generate(demo)
```

The **white** box represents **no contribution**, the **grey** box represents **minor contribution**, 
and the **black** box represents **major contribution**.

The table is nice, easy to read. The result is a `ggplot` object, so you can modify in your way!

You can also use other colors and `scale_fill_*` function from **ggplot2** to map colors:

```{r, fig.height=3}
library(ggplot2)
generate(demo, text_angle_x = 20, color_map = scale_fill_brewer(palette ="Oranges"))
```

When it is not easy to see the meaning of color, you can show the legend.

```{r, fig.height=3}
generate(demo, text_angle_x = 20, color_map = scale_fill_brewer(palette ="Set1"), show_legend = TRUE)
```


## GitHub contribution

To show how to generate numeric contribution table, here we use commit number of GitHub project as 
an example.

To get data from GitHub, I created a function `pull_github()`.

```{r}
# Github project contributions
my_contr = dplyr::tibble(
           repo = c("UCSCXenaTools", "maftools"),
           owner = c("ShixiangWang", "PoisonAlien"),
           username = "ShixiangWang",
           role = c("Developer", "Contributor"))
my_contr
contr_tb = pull_github(data = my_contr)
contr_tb
```

Now we have data format the `generate()` function can accept, show the plot!


```{r}
generate(contr_tb, show_legend = TRUE, hjust_x = 0)
```

### Palette

To change colors of contribution graph, I generated a dataset `palette` 
according to themes provided by project [github-contribution-color-graph](https://github.com/williambelle/github-contribution-color-graph).

We can show the palette and choose the color we like.

```{r, results="hide"}
show_palette()
```

Just put the name to option `palette_name`.

```{r}
generate(contr_tb, show_legend = TRUE, hjust_x = 0,
         palette_name = "psychedelic")
generate(contr_tb, show_legend = TRUE, hjust_x = 0,
         palette_name = "cyan")
```


More custom options please run `?generate` in R console.

## CRediT

**CRediT** can help assign the role, this data has been stored in this package.

```{r}
data("CRediT")
```

Show whole table.

```{r}
knitr::kable(CRediT, format = "html")
```
